Reagents: expressing and composing fine-grained concurrency

### 2011-11-01 paper/paper.tex
started related work section

\section{Related work}
\label{sec:related}

@@

pure cml~\cite{Reppy1991}

@@

Communicating transactions~\cite{Lesani2011}, 
Transaction synchronizers~\cite{Luchangco2005},
Transaction communicators~\cite{Luchangco2011},
transactional events~\cite{Donnelly2006}

@@

Paper on composing lock-free data structure operations~\cite{Cederman2010}

@@

\bibliographystyle{abbrvnat}
\bibliography{reagents}

>>>>

\newpage
\section{Related work}
\label{sec:related}

@@

Concurrent ML~\cite{Reppy1991} was designed to resolve an apparent tension
between abstraction and choice: if protocols are represented abstractly as
functions, it is impossible to express the choice of two abstract protocols.
The solution is \emph{higher-order concurrency}, in which synchronous
message-passing protocols are represented abstractly as \emph{events}.  CML's
events are built up from combinators, including a choice combinator,
communication combinators, and combinators for arbitrary computations not
involving communication.  Events are an abstract data type: externally to the
CML library, they appear as abstract, composable values.  Internally to the
library, however, events can be decomposed into their constituent combinators,
which allows CML to execute them.

Although CML events do not form a monad~\cite{?}, the basic pattern of
representing computations as abstract, composable values has become extremely
common in monadic programming

@@

Communicating transactions~\cite{Lesani2011},

Transaction synchronizers~\cite{Luchangco2005},
Transaction communicators~\cite{Luchangco2011},

transactional events~\cite{Donnelly2006}

join patterns~\cite{?}

@@

composing lock-free data structure operations~\cite{Cederman2010}

@@

\newpage
\bibliographystyle{abbrvnat}
\bibliography{reagents}
